---
title: "Lab 06 - Ugly charts and Simpson's paradox"
author: "Hannah Crawley"
date: "2.17.25"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox)
library(mosaicData) 
```

### Exercise 1

```{r}
staff <- read_csv("data/instructional-staff.csv")
```

```{r}
staff_long <- staff %>%
  pivot_longer(cols = -faculty_type, names_to = "year") %>%
  mutate(value = as.numeric(value))
```

```{r}
staff_long
```

```{r}
staff_long %>%
  ggplot(aes(x = year, y = value, group = faculty_type, color = faculty_type)) +
  geom_line() + 
  labs(Title = "Faculty Type by Year", y = "Count", x = "Year", color = "Faculty Type")
```
> Include the line plot you made above in your report and make sure the figure width is large enough to make it legible.
Also fix the title, axis labels, and legend label.


### Exercise 2

> Suppose the objective of this plot was to show that the proportion of part-time faculty have gone up over time compared to other instructional staff types. What changes would you propose making to this plot to tell this story?  

- Can filter for part-time faculty then alter the plot so that the y-axis reflects change in percentage of faculty over time and the x-axis reflects year 

### Exercise 3

> Can you help them make improve it? First, brainstorm how you would improve it. Then create the improved visualization and document your changes/decisions with bullet points. It’s ok if some of your improvements are aspirational, i.e. you don’t know how to implement it, but you think it’s a good idea. Implement what you can and leave notes identifying the aspirational improvements that could not be made. (You don’t need to recreate their plots in order to improve them) 

Potential Improvements:  
- perhaps a bar graph would help to better visualize the smoothed line graph 
- adjusting the scale of the graph so that you can see the countries that have lower fishery production
- pie plots are not extremely informative, especially those with a hole in the middle (cannot see the angles which is how one determines sizes of categories)



```{r}
fisheries <- read_csv("data/fisheries.csv")
```

```{r}
fisheries
```


```{r}
fishlong <- fisheries %>%
  pivot_longer(cols = c(aquaculture,capture, total), 
               names_to = "Type",
               values_to = "Counts")
```

``` {r}
fishlong
```

```{r}
```

