---
title: "Lab 06 - Ugly charts and Simpson's paradox"
author: "Hannah Crawley"
date: "2.17.25"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox)
library(mosaicData) 
```

### Exercise 1

```{r}
staff <- read_csv("data/instructional-staff.csv")
```

```{r}
staff_long <- staff %>%
  pivot_longer(cols = -faculty_type, names_to = "year") %>%
  mutate(value = as.numeric(value))
```

```{r}
staff_long
```

```{r}
staff_long %>%
  ggplot(aes(x = year, y = value, group = faculty_type, color = faculty_type)) +
  geom_line() + 
  labs(Title = "Faculty Type by Year", y = "Count", x = "Year", color = "Faculty Type")
```
> Include the line plot you made above in your report and make sure the figure width is large enough to make it legible.
Also fix the title, axis labels, and legend label.



### Exercise 2

> Suppose the objective of this plot was to show that the proportion of part-time faculty have gone up over time compared to other instructional staff types. What changes would you propose making to this plot to tell this story?

### Exercise 3

...

Add exercise headings as needed.
